---
title: "Polishing analysis"
date: "2021-08-07"
author: "Ryan Wick"
output:
  html_document:
    pandoc_args: ["+RTS", "-K64m", "-RTS", "--self-contained",]
    df_print: paged
    keep_md: false
    toc: true
    toc_float: true
    code_folding: hide
---


# Introduction

This knitr report aims to use real read sets to test the short-read polishers. It is based on the assumption that a closely related group of genomes should become more similar to each other as they are more accurately polished. So I'll polish the genomes using different tools and then quantify their accuracy using the total within-group distance. It's sort of like the Trycycler real read tests, but instead of pairs of identical genomes, it's groups of similar genomes.




# Setup

Load some R packages and set notebook options.

```{r collapse=TRUE}
library(tidyverse)
library(knitr)
library(ggforce)
library(cowplot)
library(colorspace)
library(RColorBrewer)
library(readxl)

opts_chunk$set(dpi=300, fig.path='../plots/', echo=TRUE, dev=c('png','pdf'), warning=FALSE, message=FALSE)
pdf.options(useDingbats = FALSE)
```

I stored a few paths (specific to my Nectar instance) in Bash variables for use throughout this analysis.
```{bash eval=FALSE}
base_dir=/home/ubuntu/hybrid_polishing/real_read_tests
script_dir=/home/ubuntu/hybrid_polishing/scripts
wrapper_dir=/home/ubuntu/hybrid_polishing/polisher_wrappers
```


## Colours

```{r colour_legend, fig.width = 4, fig.height = 6, useDingbats = FALSE, out.width = '200px'}
# hue_list <- c(0, 0.5, 0.25, 0.75,
#               0.125, 0.625, 0.375, 0.875,
#               0.0625, 0.5625, 0.3125, 0.8125, 0.1875, 0.6875, 0.4375, 0.9375,
#               0.03125, 0.53125, 0.28125, 0.78125, 0.15625, 0.65625, 0.40625, 0.90625, 0.09375, 0.59375, 0.34375, 0.84375, 0.21875, 0.71875, 0.46875, 0.96875)
# colour_list <- hsv(hue_list, 0.6, 0.9)

# consent = colour_list[1]
# flye = colour_list[2]
# hypo = colour_list[3]
# nextpolish = colour_list[4]
# marginpolish = colour_list[5]
# medaka = colour_list[6]
# ntedit = colour_list[7]
# pepper = colour_list[8]
# pilon = colour_list[9]
# polca = colour_list[10]
# polypolish = colour_list[11]
# racon = colour_list[12]
# wtpoa = colour_list[13]

colour_list <- brewer.pal(n = 8, name = "Set2")

hypo = colour_list[1]
nextpolish = colour_list[2]
ntedit = colour_list[3]
pilon = colour_list[4]
polca = colour_list[5]
polypolish = colour_list[6]
racon = colour_list[7]
wtpoa = colour_list[8]

c = c("Trycycler" = "#cccccc",
      
      "Trycycler+Medaka-long" = "#cccccc",
      
      "Trycycler+Medaka-long+HyPo-short" = hypo,
      "Trycycler+Medaka-long+HyPo-short+HyPo-short" = hypo,
      "Trycycler+Medaka-long+HyPo-short+HyPo-short+HyPo-short" = hypo,

      "Trycycler+Medaka-long+NextPolish-short" = nextpolish,
      "Trycycler+Medaka-long+NextPolish-short+NextPolish-short" = nextpolish,
      "Trycycler+Medaka-long+NextPolish-short+NextPolish-short+NextPolish-short" = nextpolish,

      "Trycycler+Medaka-long+ntEdit-short" = ntedit,
      "Trycycler+Medaka-long+ntEdit-short+ntEdit-short" = ntedit,
      "Trycycler+Medaka-long+ntEdit-short+ntEdit-short+ntEdit-short" = ntedit,
      
      "Trycycler+Medaka-long+Pilon-short" = pilon,
      "Trycycler+Medaka-long+Pilon-short+Pilon-short" = pilon,
      "Trycycler+Medaka-long+Pilon-short+Pilon-short+Pilon-short" = pilon,

      "Trycycler+Medaka-long+POLCA-short" = polca,
      "Trycycler+Medaka-long+POLCA-short+POLCA-short" = polca,
      "Trycycler+Medaka-long+POLCA-short+POLCA-short+POLCA-short" = polca,
      
      "Trycycler+Medaka-long+Polypolish-short" = polypolish,
      "Trycycler+Medaka-long+Polypolish-short+Polypolish-short" = polypolish,
      "Trycycler+Medaka-long+Polypolish-short+Polypolish-short+Polypolish-short" = polypolish,
      
      "Trycycler+Medaka-long+Racon-short" = racon,
      "Trycycler+Medaka-long+Racon-short+Racon-short" = racon,
      "Trycycler+Medaka-long+Racon-short+Racon-short+Racon-short" = racon,

      "Trycycler+Medaka-long+wtpoa-short" = wtpoa,
      "Trycycler+Medaka-long+wtpoa-short+wtpoa-short" = wtpoa,
      "Trycycler+Medaka-long+wtpoa-short+wtpoa-short+wtpoa-short" = wtpoa,
      
      "Trycycler+Medaka-long+Polypolish-short+POLCA-short" = polca
      )

# Make a colour scale for ggplot2:
polisher_colours <- scale_colour_manual(values = c)
```



# Read prep

Make some directories
```{bash eval=FALSE}
cd "$base_dir"
mkdir Acinetobacter_baumannii_J9
mkdir Citrobacter_koseri_MINF_9D
mkdir Enterobacter_kobei_MSB1_1B
mkdir Haemophilus_M1C132_1
mkdir Klebsiella_oxytoca_MSB1_2C
mkdir Klebsiella_variicola_INF345

cd "$base_dir"
for s in Acinetobacter_baumannii_J9 Citrobacter_koseri_MINF_9D Enterobacter_kobei_MSB1_1B Haemophilus_M1C132_1 Klebsiella_oxytoca_MSB1_2C Klebsiella_variicola_INF345; do
    mkdir "$s"
done
for s in Acinetobacter_baumannii_J9 Citrobacter_koseri_MINF_9D Enterobacter_kobei_MSB1_1B Haemophilus_M1C132_1 Klebsiella_oxytoca_MSB1_2C Klebsiella_variicola_INF345; do
    cd "$base_dir"/"$s"
    mkdir a b c d
    mkdir a/reads b/reads c/reads d/reads
done
```

Copy Illumina reads from MASSIVE and split them into separate groups.
```{bash eval=FALSE}
cd "$base_dir"
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_1_illumina_reads/Acinetobacter_baumannii_J9/plasmids-J9_1.fastq.gz Acinetobacter_baumannii_J9/reads/illumina_ab_1.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_1_illumina_reads/Acinetobacter_baumannii_J9/plasmids-J9_2.fastq.gz Acinetobacter_baumannii_J9/reads/illumina_ab_2.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_2_illumina_reads/Acinetobacter_baumannii_J9/J9_S142_L001_R1_001.fastq.gz Acinetobacter_baumannii_J9/reads/illumina_cd_1.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_2_illumina_reads/Acinetobacter_baumannii_J9/J9_S142_L001_R2_001.fastq.gz Acinetobacter_baumannii_J9/reads/illumina_cd_2.fastq.gz

scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_1_illumina_reads/Citrobacter_koseri_MINF_9D/plasmids-MINF-9D_1.fastq.gz Citrobacter_koseri_MINF_9D/reads/illumina_ab_1.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_1_illumina_reads/Citrobacter_koseri_MINF_9D/plasmids-MINF-9D_2.fastq.gz Citrobacter_koseri_MINF_9D/reads/illumina_ab_2.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_2_illumina_reads/Citrobacter_koseri_MINF_9D/MINF-9D_S143_L001_R1_001.fastq.gz Citrobacter_koseri_MINF_9D/reads/illumina_cd_1.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_2_illumina_reads/Citrobacter_koseri_MINF_9D/MINF-9D_S143_L001_R2_001.fastq.gz Citrobacter_koseri_MINF_9D/reads/illumina_cd_2.fastq.gz

scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_1_illumina_reads/Enterobacter_kobei_MSB1_1B/plasmids-MSB1-1B_1.fastq.gz Enterobacter_kobei_MSB1_1B/reads/illumina_ab_1.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_1_illumina_reads/Enterobacter_kobei_MSB1_1B/plasmids-MSB1-1B_2.fastq.gz Enterobacter_kobei_MSB1_1B/reads/illumina_ab_2.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_2_illumina_reads/Enterobacter_kobei_MSB1_1B/MSB1-1B_S144_L001_R1_001.fastq.gz Enterobacter_kobei_MSB1_1B/reads/illumina_cd_1.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_2_illumina_reads/Enterobacter_kobei_MSB1_1B/MSB1-1B_S144_L001_R2_001.fastq.gz Enterobacter_kobei_MSB1_1B/reads/illumina_cd_2.fastq.gz

scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_1_illumina_reads/Haemophilus_unknown_M1C132_1/plasmids-MIC132-1_1.fastq.gz Haemophilus_M1C132_1/reads/illumina_ab_1.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_1_illumina_reads/Haemophilus_unknown_M1C132_1/plasmids-MIC132-1_2.fastq.gz Haemophilus_M1C132_1/reads/illumina_ab_2.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_2_illumina_reads/Haemophilus_unknown_M1C132_1/M1C132-1_S145_L001_R1_001.fastq.gz Haemophilus_M1C132_1/reads/illumina_cd_1.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_2_illumina_reads/Haemophilus_unknown_M1C132_1/M1C132-1_S145_L001_R2_001.fastq.gz Haemophilus_M1C132_1/reads/illumina_cd_2.fastq.gz

scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_1_illumina_reads/Klebsiella_oxytoca_MSB1_2C/plasmids-MSB1-2C_1.fastq.gz Klebsiella_oxytoca_MSB1_2C/reads/illumina_ab_1.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_1_illumina_reads/Klebsiella_oxytoca_MSB1_2C/plasmids-MSB1-2C_2.fastq.gz Klebsiella_oxytoca_MSB1_2C/reads/illumina_ab_2.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_2_illumina_reads/Klebsiella_oxytoca_MSB1_2C/MSB1-2C_S146_L001_R1_001.fastq.gz Klebsiella_oxytoca_MSB1_2C/reads/illumina_cd_1.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_2_illumina_reads/Klebsiella_oxytoca_MSB1_2C/MSB1-2C_S146_L001_R2_001.fastq.gz Klebsiella_oxytoca_MSB1_2C/reads/illumina_cd_2.fastq.gz

scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_1_illumina_reads/Klebsiella_variicola_INF345/plasmids-INF345_1.fastq.gz Klebsiella_variicola_INF345/reads/illumina_ab_1.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_1_illumina_reads/Klebsiella_variicola_INF345/plasmids-INF345_2.fastq.gz Klebsiella_variicola_INF345/reads/illumina_ab_2.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_2_illumina_reads/Klebsiella_variicola_INF345/INF345_S147_L001_R1_001.fastq.gz Klebsiella_variicola_INF345/reads/illumina_cd_1.fastq.gz
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/tech_rep_2_illumina_reads/Klebsiella_variicola_INF345/INF345_S147_L001_R2_001.fastq.gz Klebsiella_variicola_INF345/reads/illumina_cd_2.fastq.gz

gunzip */reads/*.fastq.gz

cd "$base_dir"/Acinetobacter_baumannii_J9/reads
a_count=1557613; b_count=1557613
seqtk mergepe illumina_ab_1.fastq illumina_ab_2.fastq | paste - - - - - - - - | shuf > temp_merged.fastq
head -n "$a_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_a_1.fastq.gz
head -n "$a_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_a_2.fastq.gz
tail -n "$b_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_b_1.fastq.gz
tail -n "$b_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_b_2.fastq.gz
c_count=641932; d_count=641931
seqtk mergepe illumina_cd_1.fastq illumina_cd_2.fastq | paste - - - - - - - - | shuf > temp_merged.fastq
head -n "$c_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_c_1.fastq.gz
head -n "$c_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_c_2.fastq.gz
tail -n "$d_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_d_1.fastq.gz
tail -n "$d_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_d_2.fastq.gz
rm temp_merged.fastq

cd "$base_dir"/Citrobacter_koseri_MINF_9D/reads
a_count=1142150; b_count=1142150
seqtk mergepe illumina_ab_1.fastq illumina_ab_2.fastq | paste - - - - - - - - | shuf > temp_merged.fastq
head -n "$a_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_a_1.fastq.gz
head -n "$a_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_a_2.fastq.gz
tail -n "$b_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_b_1.fastq.gz
tail -n "$b_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_b_2.fastq.gz
c_count=799294; d_count=799294
seqtk mergepe illumina_cd_1.fastq illumina_cd_2.fastq | paste - - - - - - - - | shuf > temp_merged.fastq
head -n "$c_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_c_1.fastq.gz
head -n "$c_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_c_2.fastq.gz
tail -n "$d_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_d_1.fastq.gz
tail -n "$d_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_d_2.fastq.gz
rm temp_merged.fastq

cd "$base_dir"/Enterobacter_kobei_MSB1_1B/reads
a_count=1023434; b_count=1023433
seqtk mergepe illumina_ab_1.fastq illumina_ab_2.fastq | paste - - - - - - - - | shuf > temp_merged.fastq
head -n "$a_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_a_1.fastq.gz
head -n "$a_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_a_2.fastq.gz
tail -n "$b_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_b_1.fastq.gz
tail -n "$b_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_b_2.fastq.gz
c_count=801044; d_count=801044
seqtk mergepe illumina_cd_1.fastq illumina_cd_2.fastq | paste - - - - - - - - | shuf > temp_merged.fastq
head -n "$c_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_c_1.fastq.gz
head -n "$c_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_c_2.fastq.gz
tail -n "$d_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_d_1.fastq.gz
tail -n "$d_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_d_2.fastq.gz
rm temp_merged.fastq

cd "$base_dir"/Haemophilus_M1C132_1/reads
a_count=991749; b_count=991749
seqtk mergepe illumina_ab_1.fastq illumina_ab_2.fastq | paste - - - - - - - - | shuf > temp_merged.fastq
head -n "$a_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_a_1.fastq.gz
head -n "$a_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_a_2.fastq.gz
tail -n "$b_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_b_1.fastq.gz
tail -n "$b_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_b_2.fastq.gz
c_count=790461; d_count=790460
seqtk mergepe illumina_cd_1.fastq illumina_cd_2.fastq | paste - - - - - - - - | shuf > temp_merged.fastq
head -n "$c_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_c_1.fastq.gz
head -n "$c_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_c_2.fastq.gz
tail -n "$d_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_d_1.fastq.gz
tail -n "$d_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_d_2.fastq.gz
rm temp_merged.fastq

cd "$base_dir"/Klebsiella_oxytoca_MSB1_2C/reads
a_count=1818842; b_count=1818841
seqtk mergepe illumina_ab_1.fastq illumina_ab_2.fastq | paste - - - - - - - - | shuf > temp_merged.fastq
head -n "$a_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_a_1.fastq.gz
head -n "$a_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_a_2.fastq.gz
tail -n "$b_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_b_1.fastq.gz
tail -n "$b_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_b_2.fastq.gz
c_count=733390; d_count=733389
seqtk mergepe illumina_cd_1.fastq illumina_cd_2.fastq | paste - - - - - - - - | shuf > temp_merged.fastq
head -n "$c_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_c_1.fastq.gz
head -n "$c_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_c_2.fastq.gz
tail -n "$d_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_d_1.fastq.gz
tail -n "$d_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_d_2.fastq.gz
rm temp_merged.fastq

cd "$base_dir"/Klebsiella_variicola_INF345/reads
a_count=833289; b_count=833289
seqtk mergepe illumina_ab_1.fastq illumina_ab_2.fastq | paste - - - - - - - - | shuf > temp_merged.fastq
head -n "$a_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_a_1.fastq.gz
head -n "$a_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_a_2.fastq.gz
tail -n "$b_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_b_1.fastq.gz
tail -n "$b_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_b_2.fastq.gz
c_count=829561; d_count=829561
seqtk mergepe illumina_cd_1.fastq illumina_cd_2.fastq | paste - - - - - - - - | shuf > temp_merged.fastq
head -n "$c_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_c_1.fastq.gz
head -n "$c_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_c_2.fastq.gz
tail -n "$d_count" temp_merged.fastq | cut -f 1-4 | tr "\t" "\n" | gzip > illumina_d_1.fastq.gz
tail -n "$d_count" temp_merged.fastq | cut -f 5-8 | tr "\t" "\n" | gzip > illumina_d_2.fastq.gz
rm temp_merged.fastq

# Sanity check - make sure split worked as expected.
for s in Acinetobacter_baumannii_J9 Citrobacter_koseri_MINF_9D Enterobacter_kobei_MSB1_1B Haemophilus_M1C132_1 Klebsiella_oxytoca_MSB1_2C Klebsiella_variicola_INF345; do
    cd "$base_dir"/"$s"/reads
    printf "\n"$s
    printf "\nAB\n"
    cat illumina_ab_1.fastq | paste - - - - | wc -l
    zcat illumina_a_1.fastq.gz illumina_b_1.fastq.gz | paste - - - - | wc -l
    cat illumina_ab_2.fastq | paste - - - - | wc -l
    zcat illumina_a_2.fastq.gz illumina_b_2.fastq.gz | paste - - - - | wc -l
    diff <(cat illumina_ab_1.fastq | paste - - - - | cut -f1 -d$'\t' | sort) <(zcat illumina_a_1.fastq.gz illumina_b_1.fastq.gz | paste - - - - | cut -f1 -d$'\t' | sort)
    printf "\nCD\n"
    cat illumina_cd_1.fastq | paste - - - - | wc -l
    zcat illumina_c_1.fastq.gz illumina_d_1.fastq.gz | paste - - - - | wc -l
    cat illumina_cd_2.fastq | paste - - - - | wc -l
    zcat illumina_c_2.fastq.gz illumina_d_2.fastq.gz | paste - - - - | wc -l
    diff <(cat illumina_cd_1.fastq | paste - - - - | cut -f1 -d$'\t' | sort) <(zcat illumina_c_1.fastq.gz illumina_d_1.fastq.gz | paste - - - - | cut -f1 -d$'\t' | sort)
    printf "\n"
done

# Clean up before-split read files.
cd "$base_dir"
rm */reads/illumina_ab_1.fastq
rm */reads/illumina_cd_1.fastq
rm */reads/illumina_ab_2.fastq
rm */reads/illumina_cd_2.fastq
```

Illumina read QC.
```{bash eval=FALSE}
for s in Acinetobacter_baumannii_J9 Citrobacter_koseri_MINF_9D Enterobacter_kobei_MSB1_1B Haemophilus_M1C132_1 Klebsiella_oxytoca_MSB1_2C Klebsiella_variicola_INF345; do
    cd "$base_dir"/"$s"/reads
    for group in a b c d; do
        fastp --in1 illumina_"$group"_1.fastq.gz --in2 illumina_"$group"_2.fastq.gz --out1 "$base_dir"/"$s"/"$group"/reads/illumina_1.fastq.gz --out2 "$base_dir"/"$s"/"$group"/reads/illumina_2.fastq.gz --unpaired1 "$base_dir"/"$s"/"$group"/reads/illumina_u.fastq.gz --unpaired2 "$base_dir"/"$s"/"$group"/reads/illumina_u.fastq.gz
        mv fastp.html fastp.json "$base_dir"/"$s"/"$group"/reads
    done
done

for s in Acinetobacter_baumannii_J9 Citrobacter_koseri_MINF_9D Enterobacter_kobei_MSB1_1B Haemophilus_M1C132_1 Klebsiella_oxytoca_MSB1_2C Klebsiella_variicola_INF345; do
    cd "$base_dir"/"$s"/reads
    mv illumina_a_1.fastq.gz ../a/reads/illumina_raw_1.fastq.gz
    mv illumina_a_2.fastq.gz ../a/reads/illumina_raw_2.fastq.gz
    mv illumina_b_1.fastq.gz ../b/reads/illumina_raw_1.fastq.gz
    mv illumina_b_2.fastq.gz ../b/reads/illumina_raw_2.fastq.gz
    mv illumina_c_1.fastq.gz ../c/reads/illumina_raw_1.fastq.gz
    mv illumina_c_2.fastq.gz ../c/reads/illumina_raw_2.fastq.gz
    mv illumina_d_1.fastq.gz ../d/reads/illumina_raw_1.fastq.gz
    mv illumina_d_2.fastq.gz ../d/reads/illumina_raw_2.fastq.gz
    cd "$base_dir"/"$s"
    rmdir reads
done
```


Copy Nanopore reads from MASSIVE.
```{bash eval=FALSE}
cd "$base_dir"

scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-01-16_plasmid_ligation/basecalling_2021_guppy_v5.0.7_sup/barcode01.fastq.gz Acinetobacter_baumannii_J9/a/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-01-16_plasmid_rapid/basecalling_2021_guppy_v5.0.7_sup/barcode01.fastq.gz Acinetobacter_baumannii_J9/b/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-06-10_small_plasmid_ligation_02/basecalling_2021_guppy_v5.0.7_sup/barcode01.fastq.gz Acinetobacter_baumannii_J9/c/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-06-09_small_plasmid_rapid_02/basecalling_2021_guppy_v5.0.7_sup/barcode01.fastq.gz Acinetobacter_baumannii_J9/d/reads/nanopore.fastq.gz

scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-01-16_plasmid_ligation/basecalling_2021_guppy_v5.0.7_sup/barcode02.fastq.gz Citrobacter_koseri_MINF_9D/a/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-01-16_plasmid_rapid/basecalling_2021_guppy_v5.0.7_sup/barcode02.fastq.gz Citrobacter_koseri_MINF_9D/b/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-06-10_small_plasmid_ligation_02/basecalling_2021_guppy_v5.0.7_sup/barcode02.fastq.gz Citrobacter_koseri_MINF_9D/c/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-06-09_small_plasmid_rapid_02/basecalling_2021_guppy_v5.0.7_sup/barcode02.fastq.gz Citrobacter_koseri_MINF_9D/d/reads/nanopore.fastq.gz

scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-01-16_plasmid_ligation/basecalling_2021_guppy_v5.0.7_sup/barcode03.fastq.gz Enterobacter_kobei_MSB1_1B/a/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-01-16_plasmid_rapid/basecalling_2021_guppy_v5.0.7_sup/barcode03.fastq.gz Enterobacter_kobei_MSB1_1B/b/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-06-10_small_plasmid_ligation_02/basecalling_2021_guppy_v5.0.7_sup/barcode03.fastq.gz Enterobacter_kobei_MSB1_1B/c/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-06-09_small_plasmid_rapid_02/basecalling_2021_guppy_v5.0.7_sup/barcode03.fastq.gz Enterobacter_kobei_MSB1_1B/d/reads/nanopore.fastq.gz

scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-01-16_plasmid_ligation/basecalling_2021_guppy_v5.0.7_sup/barcode04.fastq.gz Haemophilus_M1C132_1/a/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-01-16_plasmid_rapid/basecalling_2021_guppy_v5.0.7_sup/barcode04.fastq.gz Haemophilus_M1C132_1/b/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-06-10_small_plasmid_ligation_02/basecalling_2021_guppy_v5.0.7_sup/barcode04.fastq.gz Haemophilus_M1C132_1/c/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-06-09_small_plasmid_rapid_02/basecalling_2021_guppy_v5.0.7_sup/barcode04.fastq.gz Haemophilus_M1C132_1/d/reads/nanopore.fastq.gz

scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-01-16_plasmid_ligation/basecalling_2021_guppy_v5.0.7_sup/barcode05.fastq.gz Klebsiella_oxytoca_MSB1_2C/a/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-01-16_plasmid_rapid/basecalling_2021_guppy_v5.0.7_sup/barcode05.fastq.gz Klebsiella_oxytoca_MSB1_2C/b/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-06-10_small_plasmid_ligation_02/basecalling_2021_guppy_v5.0.7_sup/barcode05.fastq.gz Klebsiella_oxytoca_MSB1_2C/c/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-06-09_small_plasmid_rapid_02/basecalling_2021_guppy_v5.0.7_sup/barcode05.fastq.gz Klebsiella_oxytoca_MSB1_2C/d/reads/nanopore.fastq.gz

scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-01-16_plasmid_ligation/basecalling_2021_guppy_v5.0.7_sup/barcode07.fastq.gz Klebsiella_variicola_INF345/a/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-01-16_plasmid_rapid/basecalling_2021_guppy_v5.0.7_sup/barcode07.fastq.gz Klebsiella_variicola_INF345/b/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-06-10_small_plasmid_ligation_02/basecalling_2021_guppy_v5.0.7_sup/barcode07.fastq.gz Klebsiella_variicola_INF345/c/reads/nanopore.fastq.gz
scp dtn:/mnt/vault2_holt/vault/instruments/minion/2020-06-09_small_plasmid_rapid_02/basecalling_2021_guppy_v5.0.7_sup/barcode07.fastq.gz Klebsiella_variicola_INF345/d/reads/nanopore.fastq.gz

# There were a couple rapid reads of highly repetitive junk that made Flye hang for days, so I had to track them down and remove them:
cd "$base_dir"/Haemophilus_M1C132_1/reads
zcat nanopore_d.fastq.gz | paste - - - - | grep -v -P "5ef0247e-3106-4203-852f-79d78afdbdde|06ae7b30-16ea-4238-8523-ad85a1e47b0f" | tr "\t" "\n" | gzip > nanopore_d_filter.fastq.gz
mv nanopore_d_filter.fastq.gz nanopore_d.fastq.gz
```

Get reference genomes for each (from small plasmid paper):
```{bash eval=FALSE}
cd "$base_dir"
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/assemblies/Acinetobacter_baumannii_J9.fasta Acinetobacter_baumannii_J9/reference.fasta
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/assemblies/Citrobacter_koseri_MINF_9D.fasta Citrobacter_koseri_MINF_9D/reference.fasta
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/assemblies/Enterobacter_kobei_MSB1_1B.fasta Enterobacter_kobei_MSB1_1B/reference.fasta
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/assemblies/Haemophilus_unknown_M1C132_1.fasta Haemophilus_M1C132_1/reference.fasta
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/assemblies/Klebsiella_oxytoca_MSB1_2C.fasta Klebsiella_oxytoca_MSB1_2C/reference.fasta
scp dtn:/projects/js66/individuals/ryan/Small_plasmid_Nanopore/assemblies/Klebsiella_variicola_INF345.fasta Klebsiella_variicola_INF345/reference.fasta

for s in Acinetobacter_baumannii_J9 Citrobacter_koseri_MINF_9D Enterobacter_kobei_MSB1_1B Haemophilus_M1C132_1 Klebsiella_oxytoca_MSB1_2C Klebsiella_variicola_INF345; do
    cd "$base_dir"/"$s"
    head -n2 reference.fasta > reference_chromosome.fasta
done
```


# Initial long-read assembly

Filtlong.
```{bash eval=FALSE}
for i in Acinetobacter_baumannii_J9/a Acinetobacter_baumannii_J9/b Acinetobacter_baumannii_J9/c Acinetobacter_baumannii_J9/d Citrobacter_koseri_MINF_9D/a Citrobacter_koseri_MINF_9D/b Citrobacter_koseri_MINF_9D/c Citrobacter_koseri_MINF_9D/d Enterobacter_kobei_MSB1_1B/a Enterobacter_kobei_MSB1_1B/b Enterobacter_kobei_MSB1_1B/c Enterobacter_kobei_MSB1_1B/d Haemophilus_M1C132_1/a Haemophilus_M1C132_1/b Haemophilus_M1C132_1/c Haemophilus_M1C132_1/d Klebsiella_oxytoca_MSB1_2C/a Klebsiella_oxytoca_MSB1_2C/b Klebsiella_oxytoca_MSB1_2C/c Klebsiella_oxytoca_MSB1_2C/d Klebsiella_variicola_INF345/a Klebsiella_variicola_INF345/b Klebsiella_variicola_INF345/c Klebsiella_variicola_INF345/d; do
    cd "$base_dir"/"$i"
    filtlong --min_length 1000 --keep_percent 95 reads/nanopore.fastq.gz > reads.fastq
done

# Might need a little bit more filtering for Haemophilus_M1C132_1/a, which had shorter reads than the rest.
```

Trycycler subsampling (needed to tweak `--min_read_depth` for a few read sets with low depth).
```{bash eval=FALSE}
cd "$base_dir"/Acinetobacter_baumannii_J9/a
trycycler subsample --genome_size 3949783 --reads reads.fastq --out_dir read_subsets
cd "$base_dir"/Acinetobacter_baumannii_J9/b
trycycler subsample --genome_size 3949783 --reads reads.fastq --out_dir read_subsets --min_read_depth 15
cd "$base_dir"/Acinetobacter_baumannii_J9/c
trycycler subsample --genome_size 3949783 --reads reads.fastq --out_dir read_subsets
cd "$base_dir"/Acinetobacter_baumannii_J9/d
trycycler subsample --genome_size 3949783 --reads reads.fastq --out_dir read_subsets

cd "$base_dir"/Citrobacter_koseri_MINF_9D/a
trycycler subsample --genome_size 4833164 --reads reads.fastq --out_dir read_subsets
cd "$base_dir"/Citrobacter_koseri_MINF_9D/b
trycycler subsample --genome_size 4833164 --reads reads.fastq --out_dir read_subsets
cd "$base_dir"/Citrobacter_koseri_MINF_9D/c
trycycler subsample --genome_size 4833164 --reads reads.fastq --out_dir read_subsets
cd "$base_dir"/Citrobacter_koseri_MINF_9D/d
trycycler subsample --genome_size 4833164 --reads reads.fastq --out_dir read_subsets

cd "$base_dir"/Enterobacter_kobei_MSB1_1B/a
trycycler subsample --genome_size 5093568 --reads reads.fastq --out_dir read_subsets
cd "$base_dir"/Enterobacter_kobei_MSB1_1B/b
trycycler subsample --genome_size 5093568 --reads reads.fastq --out_dir read_subsets --min_read_depth 15
cd "$base_dir"/Enterobacter_kobei_MSB1_1B/c
trycycler subsample --genome_size 5093568 --reads reads.fastq --out_dir read_subsets
cd "$base_dir"/Enterobacter_kobei_MSB1_1B/d
trycycler subsample --genome_size 5093568 --reads reads.fastq --out_dir read_subsets

cd "$base_dir"/Haemophilus_M1C132_1/a
trycycler subsample --genome_size 2125041 --reads reads.fastq --out_dir read_subsets
cd "$base_dir"/Haemophilus_M1C132_1/b
trycycler subsample --genome_size 2125041 --reads reads.fastq --out_dir read_subsets
cd "$base_dir"/Haemophilus_M1C132_1/c
trycycler subsample --genome_size 2125041 --reads reads.fastq --out_dir read_subsets
cd "$base_dir"/Haemophilus_M1C132_1/d
trycycler subsample --genome_size 2125041 --reads reads.fastq --out_dir read_subsets

cd "$base_dir"/Klebsiella_oxytoca_MSB1_2C/a
trycycler subsample --genome_size 5995635 --reads reads.fastq --out_dir read_subsets
cd "$base_dir"/Klebsiella_oxytoca_MSB1_2C/b
trycycler subsample --genome_size 5995635 --reads reads.fastq --out_dir read_subsets --min_read_depth 10
cd "$base_dir"/Klebsiella_oxytoca_MSB1_2C/c
trycycler subsample --genome_size 5995635 --reads reads.fastq --out_dir read_subsets
cd "$base_dir"/Klebsiella_oxytoca_MSB1_2C/d
trycycler subsample --genome_size 5995635 --reads reads.fastq --out_dir read_subsets

cd "$base_dir"/Klebsiella_variicola_INF345/a
trycycler subsample --genome_size 5952932 --reads reads.fastq --out_dir read_subsets
cd "$base_dir"/Klebsiella_variicola_INF345/b
trycycler subsample --genome_size 5952932 --reads reads.fastq --out_dir read_subsets
cd "$base_dir"/Klebsiella_variicola_INF345/c
trycycler subsample --genome_size 5952932 --reads reads.fastq --out_dir read_subsets
cd "$base_dir"/Klebsiella_variicola_INF345/d
trycycler subsample --genome_size 5952932 --reads reads.fastq --out_dir read_subsets
```

Assemblies for Trycycler:
```{bash eval=FALSE}
for i in Acinetobacter_baumannii_J9/a Acinetobacter_baumannii_J9/b Acinetobacter_baumannii_J9/c Acinetobacter_baumannii_J9/d Citrobacter_koseri_MINF_9D/a Citrobacter_koseri_MINF_9D/b Citrobacter_koseri_MINF_9D/c Citrobacter_koseri_MINF_9D/d Enterobacter_kobei_MSB1_1B/a Enterobacter_kobei_MSB1_1B/b Enterobacter_kobei_MSB1_1B/c Enterobacter_kobei_MSB1_1B/d Haemophilus_M1C132_1/a Haemophilus_M1C132_1/b Haemophilus_M1C132_1/c Haemophilus_M1C132_1/d Klebsiella_oxytoca_MSB1_2C/a Klebsiella_oxytoca_MSB1_2C/b Klebsiella_oxytoca_MSB1_2C/c Klebsiella_oxytoca_MSB1_2C/d Klebsiella_variicola_INF345/a Klebsiella_variicola_INF345/b Klebsiella_variicola_INF345/c Klebsiella_variicola_INF345/d; do
    cd "$base_dir"/"$i"
    mkdir assemblies
    flye --nano-hq read_subsets/sample_01.fastq --threads 32 --out-dir assembly_01 && cp assembly_01/assembly.fasta assemblies/assembly_01.fasta && rm -r assembly_01
    miniasm_and_minipolish.sh read_subsets/sample_02.fastq 32 > assembly_02.gfa && any2fasta assembly_02.gfa > assemblies/assembly_02.fasta && rm assembly_02.gfa
    raven --threads 32 read_subsets/sample_03.fastq > assemblies/assembly_03.fasta && rm raven.cereal
    flye --nano-hq read_subsets/sample_04.fastq --threads 32 --out-dir assembly_04 && cp assembly_04/assembly.fasta assemblies/assembly_04.fasta && rm -r assembly_04
    miniasm_and_minipolish.sh read_subsets/sample_05.fastq 32 > assembly_05.gfa && any2fasta assembly_05.gfa > assemblies/assembly_05.fasta && rm assembly_05.gfa
    raven --threads 32 read_subsets/sample_06.fastq > assemblies/assembly_06.fasta && rm raven.cereal
    flye --nano-hq read_subsets/sample_07.fastq --threads 32 --out-dir assembly_07 && cp assembly_07/assembly.fasta assemblies/assembly_07.fasta && rm -r assembly_07
    miniasm_and_minipolish.sh read_subsets/sample_08.fastq 32 > assembly_08.gfa && any2fasta assembly_08.gfa > assemblies/assembly_08.fasta && rm assembly_08.gfa
    raven --threads 32 read_subsets/sample_09.fastq > assemblies/assembly_09.fasta && rm raven.cereal
    flye --nano-hq read_subsets/sample_10.fastq --threads 32 --out-dir assembly_10 && cp assembly_10/assembly.fasta assemblies/assembly_10.fasta && rm -r assembly_10
    miniasm_and_minipolish.sh read_subsets/sample_11.fastq 32 > assembly_11.gfa && any2fasta assembly_11.gfa > assemblies/assembly_11.fasta && rm assembly_11.gfa
    raven --threads 32 read_subsets/sample_12.fastq > assemblies/assembly_12.fasta && rm raven.cereal
done
```

Trycycler cluster:
```{bash eval=FALSE}
for i in Acinetobacter_baumannii_J9/a Acinetobacter_baumannii_J9/b Acinetobacter_baumannii_J9/c Acinetobacter_baumannii_J9/d Citrobacter_koseri_MINF_9D/a Citrobacter_koseri_MINF_9D/b Citrobacter_koseri_MINF_9D/c Citrobacter_koseri_MINF_9D/d Enterobacter_kobei_MSB1_1B/a Enterobacter_kobei_MSB1_1B/b Enterobacter_kobei_MSB1_1B/c Enterobacter_kobei_MSB1_1B/d Haemophilus_M1C132_1/a Haemophilus_M1C132_1/b Haemophilus_M1C132_1/c Haemophilus_M1C132_1/d Klebsiella_oxytoca_MSB1_2C/a Klebsiella_oxytoca_MSB1_2C/b Klebsiella_oxytoca_MSB1_2C/c Klebsiella_oxytoca_MSB1_2C/d Klebsiella_variicola_INF345/a Klebsiella_variicola_INF345/b Klebsiella_variicola_INF345/c Klebsiella_variicola_INF345/d; do
    cd "$base_dir"/"$i"
    trycycler cluster --threads 32 --assemblies assemblies/*.fasta --reads reads.fastq --out_dir trycycler 2> trycycler_cluster.out
done
```

For each isolate:
```{bash eval=FALSE}
cd "$base_dir"/"$i"
# Check clusters
trycycler reconcile --max_indel_size 1000 --threads 32 --reads reads.fastq --cluster_dir trycycler/cluster_001  # For each good cluster

for c in trycycler/cluster_*; do trycycler msa --cluster_dir "$c" --threads 32; done
trycycler partition --reads reads.fastq --cluster_dirs trycycler/cluster_* --threads 32
for c in trycycler/cluster_*; do trycycler consensus --cluster_dir "$c" --threads 32; done

for c in trycycler/cluster_*; do
    medaka_consensus -i "$c"/4_reads.fastq -d "$c"/7_final_consensus.fasta -o "$c"/medaka -m r941_min_sup_g507 -t 12
    mv "$c"/medaka/consensus.fasta "$c"/8_medaka.fasta
    rm -r "$c"/medaka "$c"/*.fai "$c"/*.mmi  # clean up
done

cat trycycler/cluster_*/7_final_consensus.fasta > trycycler.fasta
cat trycycler/cluster_*/8_medaka.fasta > trycycler__medaka-long.fasta

mv trycycler_cluster.out trycycler
mv assemblies trycycler

rm -r reads.fastq read_subsets
rm trycycler/cluster_*/4_reads.fastq
```

I also did a short-read assembly with Unicycler using all Illumina reads. This wasn't really used in the analysis, but I enjoy having a short-read graph to use when manually investigating things, e.g. for identifying repeat regions:
```{bash eval=FALSE}
for s in Acinetobacter_baumannii_J9 Citrobacter_koseri_MINF_9D Enterobacter_kobei_MSB1_1B Haemophilus_M1C132_1 Klebsiella_oxytoca_MSB1_2C Klebsiella_variicola_INF345; do
    cd "$base_dir"/"$s"
    cat a/reads/illumina_1.fastq.gz b/reads/illumina_1.fastq.gz c/reads/illumina_1.fastq.gz d/reads/illumina_1.fastq.gz > temp_illumina_1.fastq.gz
    cat a/reads/illumina_2.fastq.gz b/reads/illumina_2.fastq.gz c/reads/illumina_2.fastq.gz d/reads/illumina_2.fastq.gz > temp_illumina_2.fastq.gz
    unicycler -1 temp_illumina_1.fastq.gz -2 temp_illumina_2.fastq.gz -o unicycler --threads 32 --no_pilon --no_rotate --no_correct
    rm temp_illumina_1.fastq.gz temp_illumina_2.fastq.gz
done
```




# Short-read polishing

Before beginning, I had to fix up the Illumina read names to ensure that they ended in '/1' or '/2'. This is mainly for Racon polishing where the reads are merged and we need to prevent duplicate read names in the merged file.

```{bash eval=FALSE}
for i in Acinetobacter_baumannii_J9/a Acinetobacter_baumannii_J9/b Acinetobacter_baumannii_J9/c Acinetobacter_baumannii_J9/d Citrobacter_koseri_MINF_9D/a Citrobacter_koseri_MINF_9D/b Citrobacter_koseri_MINF_9D/c Citrobacter_koseri_MINF_9D/d Enterobacter_kobei_MSB1_1B/a Enterobacter_kobei_MSB1_1B/b Enterobacter_kobei_MSB1_1B/c Enterobacter_kobei_MSB1_1B/d Haemophilus_M1C132_1/a Haemophilus_M1C132_1/b Haemophilus_M1C132_1/c Haemophilus_M1C132_1/d Klebsiella_oxytoca_MSB1_2C/a Klebsiella_oxytoca_MSB1_2C/b Klebsiella_oxytoca_MSB1_2C/c Klebsiella_oxytoca_MSB1_2C/d Klebsiella_variicola_INF345/a Klebsiella_variicola_INF345/b Klebsiella_variicola_INF345/c Klebsiella_variicola_INF345/d; do
    cd "$base_dir"/"$i"/reads
    echo "$i"
    cp illumina_1.fastq.gz illumina_1.fastq.gz.backup
    cp illumina_2.fastq.gz illumina_2.fastq.gz.backup
    gunzip illumina_1.fastq.gz illumina_2.fastq.gz
    sed -i 's| 1:N:0:|/1 1:N:0:|' illumina_1.fastq
    sed -i 's| 2:N:0:|/2 2:N:0:|' illumina_2.fastq
    gzip illumina_1.fastq &
    gzip illumina_2.fastq &
done
```




## Single-tool

### HyPo v1.0.3

```{bash eval=FALSE}
__conda_setup="$('/home/ubuntu/miniconda3/bin/conda' 'shell.bash' 'hook' 2> /dev/null)"
if [ $? -eq 0 ]; then
    eval "$__conda_setup"
else
    if [ -f "/home/ubuntu/miniconda3/etc/profile.d/conda.sh" ]; then
        . "/home/ubuntu/miniconda3/etc/profile.d/conda.sh"
    else
        export PATH="/home/ubuntu/miniconda3/bin:$PATH"
    fi
fi
unset __conda_setup
conda activate hypo

for i in Acinetobacter_baumannii_J9/a Acinetobacter_baumannii_J9/b Acinetobacter_baumannii_J9/c Acinetobacter_baumannii_J9/d Citrobacter_koseri_MINF_9D/a Citrobacter_koseri_MINF_9D/b Citrobacter_koseri_MINF_9D/c Citrobacter_koseri_MINF_9D/d Enterobacter_kobei_MSB1_1B/a Enterobacter_kobei_MSB1_1B/b Enterobacter_kobei_MSB1_1B/c Enterobacter_kobei_MSB1_1B/d Haemophilus_M1C132_1/a Haemophilus_M1C132_1/b Haemophilus_M1C132_1/c Haemophilus_M1C132_1/d Klebsiella_oxytoca_MSB1_2C/a Klebsiella_oxytoca_MSB1_2C/b Klebsiella_oxytoca_MSB1_2C/c Klebsiella_oxytoca_MSB1_2C/d Klebsiella_variicola_INF345/a Klebsiella_variicola_INF345/b Klebsiella_variicola_INF345/c Klebsiella_variicola_INF345/d; do
    cd "$base_dir"/"$i"
    r1=reads/illumina_1.fastq.gz
    r2=reads/illumina_2.fastq.gz
    "$wrapper_dir"/hypo-short.sh trycycler__medaka-long.fasta "$r1" "$r2" trycycler__medaka-long__hypo-short
    "$wrapper_dir"/hypo-short.sh trycycler__medaka-long__hypo-short.fasta "$r1" "$r2" trycycler__medaka-long__hypo-short__hypo-short
    "$wrapper_dir"/hypo-short.sh trycycler__medaka-long__hypo-short__hypo-short.fasta "$r1" "$r2" trycycler__medaka-long__hypo-short__hypo-short__hypo-short
done
```


### NextPolish v1.3.1

```{bash eval=FALSE}
for i in Acinetobacter_baumannii_J9/a Acinetobacter_baumannii_J9/b Acinetobacter_baumannii_J9/c Acinetobacter_baumannii_J9/d Citrobacter_koseri_MINF_9D/a Citrobacter_koseri_MINF_9D/b Citrobacter_koseri_MINF_9D/c Citrobacter_koseri_MINF_9D/d Enterobacter_kobei_MSB1_1B/a Enterobacter_kobei_MSB1_1B/b Enterobacter_kobei_MSB1_1B/c Enterobacter_kobei_MSB1_1B/d Haemophilus_M1C132_1/a Haemophilus_M1C132_1/b Haemophilus_M1C132_1/c Haemophilus_M1C132_1/d Klebsiella_oxytoca_MSB1_2C/a Klebsiella_oxytoca_MSB1_2C/b Klebsiella_oxytoca_MSB1_2C/c Klebsiella_oxytoca_MSB1_2C/d Klebsiella_variicola_INF345/a Klebsiella_variicola_INF345/b Klebsiella_variicola_INF345/c Klebsiella_variicola_INF345/d; do
    cd "$base_dir"/"$i"
    r1=reads/illumina_1.fastq.gz
    r2=reads/illumina_2.fastq.gz
    "$wrapper_dir"/nextpolish-short.sh trycycler__medaka-long.fasta "$r1" "$r2" trycycler__medaka-long__nextpolish-short
    "$wrapper_dir"/nextpolish-short.sh trycycler__medaka-long__nextpolish-short.fasta "$r1" "$r2" trycycler__medaka-long__nextpolish-short__nextpolish-short
    "$wrapper_dir"/nextpolish-short.sh trycycler__medaka-long__nextpolish-short__nextpolish-short.fasta "$r1" "$r2" trycycler__medaka-long__nextpolish-short__nextpolish-short__nextpolish-short
done
```


### ntEdit v1.3.5

```{bash eval=FALSE}
for i in Acinetobacter_baumannii_J9/a Acinetobacter_baumannii_J9/b Acinetobacter_baumannii_J9/c Acinetobacter_baumannii_J9/d Citrobacter_koseri_MINF_9D/a Citrobacter_koseri_MINF_9D/b Citrobacter_koseri_MINF_9D/c Citrobacter_koseri_MINF_9D/d Enterobacter_kobei_MSB1_1B/a Enterobacter_kobei_MSB1_1B/b Enterobacter_kobei_MSB1_1B/c Enterobacter_kobei_MSB1_1B/d Haemophilus_M1C132_1/a Haemophilus_M1C132_1/b Haemophilus_M1C132_1/c Haemophilus_M1C132_1/d Klebsiella_oxytoca_MSB1_2C/a Klebsiella_oxytoca_MSB1_2C/b Klebsiella_oxytoca_MSB1_2C/c Klebsiella_oxytoca_MSB1_2C/d Klebsiella_variicola_INF345/a Klebsiella_variicola_INF345/b Klebsiella_variicola_INF345/c Klebsiella_variicola_INF345/d; do
    cd "$base_dir"/"$i"
    r1=reads/illumina_1.fastq.gz
    r2=reads/illumina_2.fastq.gz
    "$wrapper_dir"/ntedit-short.sh trycycler__medaka-long.fasta "$r1" "$r2" trycycler__medaka-long__ntedit-short
    "$wrapper_dir"/ntedit-short.sh trycycler__medaka-long__ntedit-short.fasta "$r1" "$r2" trycycler__medaka-long__ntedit-short__ntedit-short
    "$wrapper_dir"/ntedit-short.sh trycycler__medaka-long__ntedit-short__ntedit-short.fasta "$r1" "$r2" trycycler__medaka-long__ntedit-short__ntedit-short__ntedit-short
done
```



### Pilon v1.24

```{bash eval=FALSE}
for i in Acinetobacter_baumannii_J9/a Acinetobacter_baumannii_J9/b Acinetobacter_baumannii_J9/c Acinetobacter_baumannii_J9/d Citrobacter_koseri_MINF_9D/a Citrobacter_koseri_MINF_9D/b Citrobacter_koseri_MINF_9D/c Citrobacter_koseri_MINF_9D/d Enterobacter_kobei_MSB1_1B/a Enterobacter_kobei_MSB1_1B/b Enterobacter_kobei_MSB1_1B/c Enterobacter_kobei_MSB1_1B/d Haemophilus_M1C132_1/a Haemophilus_M1C132_1/b Haemophilus_M1C132_1/c Haemophilus_M1C132_1/d Klebsiella_oxytoca_MSB1_2C/a Klebsiella_oxytoca_MSB1_2C/b Klebsiella_oxytoca_MSB1_2C/c Klebsiella_oxytoca_MSB1_2C/d Klebsiella_variicola_INF345/a Klebsiella_variicola_INF345/b Klebsiella_variicola_INF345/c Klebsiella_variicola_INF345/d; do
    cd "$base_dir"/"$i"
    r1=reads/illumina_1.fastq.gz
    r2=reads/illumina_2.fastq.gz
    "$wrapper_dir"/pilon-short.sh trycycler__medaka-long.fasta "$r1" "$r2" trycycler__medaka-long__pilon-short
    "$wrapper_dir"/pilon-short.sh trycycler__medaka-long__pilon-short.fasta "$r1" "$r2" trycycler__medaka-long__pilon-short__pilon-short
    "$wrapper_dir"/pilon-short.sh trycycler__medaka-long__pilon-short__pilon-short.fasta "$r1" "$r2" trycycler__medaka-long__pilon-short__pilon-short__pilon-short
done
```



### POLCA v4.0.3

```{bash eval=FALSE}
for i in Acinetobacter_baumannii_J9/a Acinetobacter_baumannii_J9/b Acinetobacter_baumannii_J9/c Acinetobacter_baumannii_J9/d Citrobacter_koseri_MINF_9D/a Citrobacter_koseri_MINF_9D/b Citrobacter_koseri_MINF_9D/c Citrobacter_koseri_MINF_9D/d Enterobacter_kobei_MSB1_1B/a Enterobacter_kobei_MSB1_1B/b Enterobacter_kobei_MSB1_1B/c Enterobacter_kobei_MSB1_1B/d Haemophilus_M1C132_1/a Haemophilus_M1C132_1/b Haemophilus_M1C132_1/c Haemophilus_M1C132_1/d Klebsiella_oxytoca_MSB1_2C/a Klebsiella_oxytoca_MSB1_2C/b Klebsiella_oxytoca_MSB1_2C/c Klebsiella_oxytoca_MSB1_2C/d Klebsiella_variicola_INF345/a Klebsiella_variicola_INF345/b Klebsiella_variicola_INF345/c Klebsiella_variicola_INF345/d; do
    cd "$base_dir"/"$i"
    r1=reads/illumina_1.fastq.gz
    r2=reads/illumina_2.fastq.gz
    "$wrapper_dir"/polca-short.sh trycycler__medaka-long.fasta "$r1" "$r2" trycycler__medaka-long__polca-short
    "$wrapper_dir"/polca-short.sh trycycler__medaka-long__polca-short.fasta "$r1" "$r2" trycycler__medaka-long__polca-short__polca-short
    "$wrapper_dir"/polca-short.sh trycycler__medaka-long__polca-short__polca-short.fasta "$r1" "$r2" trycycler__medaka-long__polca-short__polca-short__polca-short
done
```



### Polypolish v0.4.3

```{bash eval=FALSE}
for i in Acinetobacter_baumannii_J9/a Acinetobacter_baumannii_J9/b Acinetobacter_baumannii_J9/c Acinetobacter_baumannii_J9/d Citrobacter_koseri_MINF_9D/a Citrobacter_koseri_MINF_9D/b Citrobacter_koseri_MINF_9D/c Citrobacter_koseri_MINF_9D/d Enterobacter_kobei_MSB1_1B/a Enterobacter_kobei_MSB1_1B/b Enterobacter_kobei_MSB1_1B/c Enterobacter_kobei_MSB1_1B/d Haemophilus_M1C132_1/a Haemophilus_M1C132_1/b Haemophilus_M1C132_1/c Haemophilus_M1C132_1/d Klebsiella_oxytoca_MSB1_2C/a Klebsiella_oxytoca_MSB1_2C/b Klebsiella_oxytoca_MSB1_2C/c Klebsiella_oxytoca_MSB1_2C/d Klebsiella_variicola_INF345/a Klebsiella_variicola_INF345/b Klebsiella_variicola_INF345/c Klebsiella_variicola_INF345/d; do
    cd "$base_dir"/"$i"
    r1=reads/illumina_1.fastq.gz
    r2=reads/illumina_2.fastq.gz
    "$wrapper_dir"/polypolish-short.sh trycycler__medaka-long.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short
    "$wrapper_dir"/polypolish-short.sh trycycler__medaka-long__polypolish-short.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short__polypolish-short
    "$wrapper_dir"/polypolish-short.sh trycycler__medaka-long__polypolish-short__polypolish-short.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short__polypolish-short__polypolish-short
done
```



### Racon v1.4.21

```{bash eval=FALSE}
for i in Acinetobacter_baumannii_J9/a Acinetobacter_baumannii_J9/b Acinetobacter_baumannii_J9/c Acinetobacter_baumannii_J9/d Citrobacter_koseri_MINF_9D/a Citrobacter_koseri_MINF_9D/b Citrobacter_koseri_MINF_9D/c Citrobacter_koseri_MINF_9D/d Enterobacter_kobei_MSB1_1B/a Enterobacter_kobei_MSB1_1B/b Enterobacter_kobei_MSB1_1B/c Enterobacter_kobei_MSB1_1B/d Haemophilus_M1C132_1/a Haemophilus_M1C132_1/b Haemophilus_M1C132_1/c Haemophilus_M1C132_1/d Klebsiella_oxytoca_MSB1_2C/a Klebsiella_oxytoca_MSB1_2C/b Klebsiella_oxytoca_MSB1_2C/c Klebsiella_oxytoca_MSB1_2C/d Klebsiella_variicola_INF345/a Klebsiella_variicola_INF345/b Klebsiella_variicola_INF345/c Klebsiella_variicola_INF345/d; do
    cd "$base_dir"/"$i"
    r1=reads/illumina_1.fastq.gz
    r2=reads/illumina_2.fastq.gz
    "$wrapper_dir"/racon-short.sh trycycler__medaka-long.fasta "$r1" "$r2" trycycler__medaka-long__racon-short
    "$wrapper_dir"/racon-short.sh trycycler__medaka-long__racon-short.fasta "$r1" "$r2" trycycler__medaka-long__racon-short__racon-short
    "$wrapper_dir"/racon-short.sh trycycler__medaka-long__racon-short__racon-short.fasta "$r1" "$r2" trycycler__medaka-long__racon-short__racon-short__racon-short
done
```



### wtpoa-cns v2.5

```{bash eval=FALSE}
for i in Acinetobacter_baumannii_J9/a Acinetobacter_baumannii_J9/b Acinetobacter_baumannii_J9/c Acinetobacter_baumannii_J9/d Citrobacter_koseri_MINF_9D/a Citrobacter_koseri_MINF_9D/b Citrobacter_koseri_MINF_9D/c Citrobacter_koseri_MINF_9D/d Enterobacter_kobei_MSB1_1B/a Enterobacter_kobei_MSB1_1B/b Enterobacter_kobei_MSB1_1B/c Enterobacter_kobei_MSB1_1B/d Haemophilus_M1C132_1/a Haemophilus_M1C132_1/b Haemophilus_M1C132_1/c Haemophilus_M1C132_1/d Klebsiella_oxytoca_MSB1_2C/a Klebsiella_oxytoca_MSB1_2C/b Klebsiella_oxytoca_MSB1_2C/c Klebsiella_oxytoca_MSB1_2C/d Klebsiella_variicola_INF345/a Klebsiella_variicola_INF345/b Klebsiella_variicola_INF345/c Klebsiella_variicola_INF345/d; do
    cd "$base_dir"/"$i"
    r1=reads/illumina_1.fastq.gz
    r2=reads/illumina_2.fastq.gz
    "$wrapper_dir"/wtpoa-short.sh trycycler__medaka-long.fasta "$r1" "$r2" trycycler__medaka-long__wtpoa-short
    "$wrapper_dir"/wtpoa-short.sh trycycler__medaka-long__wtpoa-short.fasta "$r1" "$r2" trycycler__medaka-long__wtpoa-short__wtpoa-short
    "$wrapper_dir"/wtpoa-short.sh trycycler__medaka-long__wtpoa-short__wtpoa-short.fasta "$r1" "$r2" trycycler__medaka-long__wtpoa-short__wtpoa-short__wtpoa-short
done
```



### Gather results

Get the pairwise distances for each set:
```{bash eval=FALSE}
for p in trycycler trycycler__medaka-long trycycler__medaka-long__hypo-short trycycler__medaka-long__hypo-short__hypo-short trycycler__medaka-long__hypo-short__hypo-short__hypo-short trycycler__medaka-long__nextpolish-short trycycler__medaka-long__nextpolish-short__nextpolish-short trycycler__medaka-long__nextpolish-short__nextpolish-short__nextpolish-short trycycler__medaka-long__ntedit-short trycycler__medaka-long__ntedit-short__ntedit-short trycycler__medaka-long__ntedit-short__ntedit-short__ntedit-short trycycler__medaka-long__pilon-short trycycler__medaka-long__pilon-short__pilon-short trycycler__medaka-long__pilon-short__pilon-short__pilon-short trycycler__medaka-long__polca-short trycycler__medaka-long__polca-short__polca-short trycycler__medaka-long__polca-short__polca-short__polca-short trycycler__medaka-long__polypolish-short trycycler__medaka-long__polypolish-short__polypolish-short trycycler__medaka-long__polypolish-short__polypolish-short__polypolish-short trycycler__medaka-long__racon-short trycycler__medaka-long__racon-short__racon-short trycycler__medaka-long__racon-short__racon-short__racon-short trycycler__medaka-long__wtpoa-short trycycler__medaka-long__wtpoa-short__wtpoa-short trycycler__medaka-long__wtpoa-short__wtpoa-short__wtpoa-short; do
    for i in Acinetobacter_baumannii_J9 Citrobacter_koseri_MINF_9D Enterobacter_kobei_MSB1_1B Haemophilus_M1C132_1 Klebsiella_oxytoca_MSB1_2C Klebsiella_variicola_INF345; do
        cd "$base_dir"/"$i"
        printf $i"\t"$p"\t"
        "$script_dir"/pairwise_distances.py a/"$p".fasta b/"$p".fasta c/"$p".fasta d/"$p".fasta > "$p".phylip
    done
done
```




### Plot results

```{r short_read_single_tool_first_round, fig.width = 10.5, fig.height = 5, useDingbats = FALSE}
results <- read_excel("../tables/Table_S2_real_read_results.xlsx", sheet = "Distances", col_names = TRUE)

filter(results, polishing == "Trycycler" |
                polishing == "Trycycler+Medaka-long" |
                polishing == "Trycycler+Medaka-long+HyPo-short" |
                polishing == "Trycycler+Medaka-long+NextPolish-shortt" |
                polishing == "Trycycler+Medaka-long+ntEdit-short" |
                polishing == "Trycycler+Medaka-long+Pilon-short" |
                polishing == "Trycycler+Medaka-long+POLCA-short" |
                polishing == "Trycycler+Medaka-long+Polypolish-short" |
                polishing == "Trycycler+Medaka-long+Racon-short" |
                polishing == "Trycycler+Medaka-long+wtpoa-short") -> results
results$polishing <- factor(results$polishing,
                            levels = c("Trycycler",
                                       "Trycycler+Medaka-long",
                                       "Trycycler+Medaka-long+HyPo-short",
                                       "Trycycler+Medaka-long+NextPolish-short",
                                       "Trycycler+Medaka-long+ntEdit-short",
                                       "Trycycler+Medaka-long+Pilon-short",
                                       "Trycycler+Medaka-long+POLCA-short",
                                       "Trycycler+Medaka-long+Polypolish-short",
                                       "Trycycler+Medaka-long+Racon-short",
                                       "Trycycler+Medaka-long+wtpoa-short"))
display_names <- c("Trycycler",
                   "Trycycler+Medaka",
                   "Trycycler+Medaka+HyPo",
                   "Trycycler+Medaka+NextPolish",
                   "Trycycler+Medaka+ntEdit",
                   "Trycycler+Medaka+Pilon",
                   "Trycycler+Medaka+POLCA",
                   "Trycycler+Medaka+Polypolish",
                   "Trycycler+Medaka+Racon",
                   "Trycycler+Medaka+wtpoa")
display_names <- gsub("\\+", "+\n", display_names)

set_shapes <- scale_shape_manual(values = c("Acinetobacter_baumannii_J9" = 0,
                                            "Citrobacter_koseri_MINF_9D" = 1,
                                            "Enterobacter_kobei_MSB1_1B" = 2,
                                            "Haemophilus_M1C132_1" = 3,
                                            "Klebsiella_oxytoca_MSB1_2C" = 4,
                                            "Klebsiella_variicola_INF345" = 5))

ggplot(results, aes(x=polishing, y=total_distance, colour=polishing, shape=isolate)) +
  geom_point(size=2.5, stroke=2.5) +
  polisher_colours + set_shapes + guides(colour = "none") +
  theme_bw() + theme(plot.background = element_blank()) +
  scale_x_discrete(labels = display_names) +
  scale_y_continuous(trans=scales::pseudo_log_trans(),
                     breaks = c(0, 10, 100, 1000, 10000, 100000, 1000000), minor_breaks = NULL,
                     labels = c("0", "10", "100", "1000", "10000", "100000", "1000000")) +
  coord_cartesian(ylim = c(0, 1000000)) +
  labs(title = "Real read single-tool polishing (sum of pairwise distances)", x = NULL, y = "Errors")
```

```{r short_read_single_tool_third_round, fig.width = 7.5, fig.height = 3, useDingbats = FALSE}
results <- read_excel("../tables/Table_S2_real_read_results.xlsx", sheet = "Distances", col_names = TRUE)

filter(results, polishing == "Trycycler+Medaka-long" |
                polishing == "Trycycler+Medaka-long+HyPo-short+HyPo-short+HyPo-short" |
                polishing == "Trycycler+Medaka-long+NextPolish-short+NextPolish-short+NextPolish-short" |
                polishing == "Trycycler+Medaka-long+ntEdit-short+ntEdit-short+ntEdit-short" |
                polishing == "Trycycler+Medaka-long+Pilon-short+Pilon-short+Pilon-short" |
                polishing == "Trycycler+Medaka-long+POLCA-short+POLCA-short+POLCA-short" |
                polishing == "Trycycler+Medaka-long+Polypolish-short+Polypolish-short+Polypolish-short" |
                polishing == "Trycycler+Medaka-long+Racon-short+Racon-short+Racon-short") -> results
results$polishing <- factor(results$polishing,
                            levels = c("Trycycler+Medaka-long",
                                       "Trycycler+Medaka-long+HyPo-short+HyPo-short+HyPo-short",
                                       "Trycycler+Medaka-long+NextPolish-short+NextPolish-short+NextPolish-short",
                                       "Trycycler+Medaka-long+ntEdit-short+ntEdit-short+ntEdit-short",
                                       "Trycycler+Medaka-long+Pilon-short+Pilon-short+Pilon-short",
                                       "Trycycler+Medaka-long+POLCA-short+POLCA-short+POLCA-short",
                                       "Trycycler+Medaka-long+Polypolish-short+Polypolish-short+Polypolish-short",
                                       "Trycycler+Medaka-long+Racon-short+Racon-short+Racon-short"))
display_names <- c("unpolished",
                   "HyPo\n3",
                   "NextPolish\n3",
                   "ntEdit\n3",
                   "Pilon\n3",
                   "POLCA\n3",
                   "Polypolish\n3",
                   "Racon\n3")
display_names <- gsub("\\+", "+\n", display_names)

set_shapes <- scale_shape_manual(values = c("Acinetobacter_baumannii_J9" = 0,
                                            "Citrobacter_koseri_MINF_9D" = 1,
                                            "Enterobacter_kobei_MSB1_1B" = 2,
                                            "Haemophilus_M1C132_1" = 3,
                                            "Klebsiella_oxytoca_MSB1_2C" = 4,
                                            "Klebsiella_variicola_INF345" = 5))

ggplot(results, aes(x=polishing, y=total_distance, colour=polishing, shape=isolate)) +
  geom_point(size=2.5, stroke=2.5) +
  polisher_colours + set_shapes + guides(colour = "none") +
  theme_bw() + theme(plot.background = element_blank()) +
  scale_x_discrete(labels = display_names) +
  scale_y_continuous(trans=scales::pseudo_log_trans(),
                     breaks = c(0, 10, 100, 1000, 10000, 100000, 1000000), minor_breaks = NULL,
                     labels = c("0", "10", "100", "1000", "10000", "100000", "1000000")) +
  coord_cartesian(ylim = c(0, 15000)) +
  labs(title = "Single-tool short-read polishing", x = NULL, y = "Sum of pairwise distances")
```

```{r short_read_single_tool_all_rounds, fig.width = 19, fig.height = 5, useDingbats = FALSE}
results <- read_excel("../tables/Table_S2_real_read_results.xlsx", sheet = "Distances", col_names = TRUE)

filter(results, polishing == "Trycycler+Medaka-long" |
                polishing == "Trycycler+Medaka-long+HyPo-short" | polishing == "Trycycler+Medaka-long+HyPo-short+HyPo-short" | polishing == "Trycycler+Medaka-long+HyPo-short+HyPo-short+HyPo-short" |
                polishing == "Trycycler+Medaka-long+NextPolish-short" | polishing == "Trycycler+Medaka-long+NextPolish-short+NextPolish-short" | polishing == "Trycycler+Medaka-long+NextPolish-short+NextPolish-short+NextPolish-short" |
                polishing == "Trycycler+Medaka-long+ntEdit-short" | polishing == "Trycycler+Medaka-long+ntEdit-short+ntEdit-short" | polishing == "Trycycler+Medaka-long+ntEdit-short+ntEdit-short+ntEdit-short" |
                polishing == "Trycycler+Medaka-long+Pilon-short" | polishing == "Trycycler+Medaka-long+Pilon-short+Pilon-short" | polishing == "Trycycler+Medaka-long+Pilon-short+Pilon-short+Pilon-short" |
                polishing == "Trycycler+Medaka-long+POLCA-short" | polishing == "Trycycler+Medaka-long+POLCA-short+POLCA-short" | polishing == "Trycycler+Medaka-long+POLCA-short+POLCA-short+POLCA-short" |
                polishing == "Trycycler+Medaka-long+Polypolish-short" | polishing == "Trycycler+Medaka-long+Polypolish-short+Polypolish-short" | polishing == "Trycycler+Medaka-long+Polypolish-short+Polypolish-short+Polypolish-short" |
                polishing == "Trycycler+Medaka-long+Racon-short" | polishing == "Trycycler+Medaka-long+Racon-short+Racon-short" | polishing == "Trycycler+Medaka-long+Racon-short+Racon-short+Racon-short" |
                polishing == "Trycycler+Medaka-long+wtpoa-short" | polishing == "Trycycler+Medaka-long+wtpoa-short+wtpoa-short" | polishing == "Trycycler+Medaka-long+wtpoa-short+wtpoa-short+wtpoa-short") -> results
results$polishing <- factor(results$polishing,
                            levels = c("Trycycler+Medaka-long",
                                       "Trycycler+Medaka-long+HyPo-short", "Trycycler+Medaka-long+HyPo-short+HyPo-short", "Trycycler+Medaka-long+HyPo-short+HyPo-short+HyPo-short",
                                       "Trycycler+Medaka-long+NextPolish-short", "Trycycler+Medaka-long+NextPolish-short+NextPolish-short", "Trycycler+Medaka-long+NextPolish-short+NextPolish-short+NextPolish-short",
                                       "Trycycler+Medaka-long+ntEdit-short", "Trycycler+Medaka-long+ntEdit-short+ntEdit-short", "Trycycler+Medaka-long+ntEdit-short+ntEdit-short+ntEdit-short",
                                       "Trycycler+Medaka-long+Pilon-short", "Trycycler+Medaka-long+Pilon-short+Pilon-short", "Trycycler+Medaka-long+Pilon-short+Pilon-short+Pilon-short",
                                       "Trycycler+Medaka-long+POLCA-short", "Trycycler+Medaka-long+POLCA-short+POLCA-short", "Trycycler+Medaka-long+POLCA-short+POLCA-short+POLCA-short",
                                       "Trycycler+Medaka-long+Polypolish-short", "Trycycler+Medaka-long+Polypolish-short+Polypolish-short", "Trycycler+Medaka-long+Polypolish-short+Polypolish-short+Polypolish-short",
                                       "Trycycler+Medaka-long+Racon-short", "Trycycler+Medaka-long+Racon-short+Racon-short", "Trycycler+Medaka-long+Racon-short+Racon-short+Racon-short",
                                       "Trycycler+Medaka-long+wtpoa-short", "Trycycler+Medaka-long+wtpoa-short+wtpoa-short", "Trycycler+Medaka-long+wtpoa-short+wtpoa-short+wtpoa-short"))
display_names <- c("unpolished",
                   "HyPo", "HyPo\n2", "HyPo\n3",
                   "NextPolish", "NextPolish\n2", "NextPolish\n3",
                   "ntEdit", "ntEdit\n2", "ntEdit\n3",
                   "Pilon", "Pilon\n2", "Pilon\n3",
                   "POLCA", "POLCA\n2", "POLCA\n3",
                   "Polypolish", "Polypolish\n2", "Polypolish\n3",
                   "Racon", "Racon\n2", "Racon\n3",
                   "wtpoa", "wtpoa\n2", "wtpoa\n3")
display_names <- gsub("\\+", "+\n", display_names)

set_shapes <- scale_shape_manual(values = c("Acinetobacter_baumannii_J9" = 0,
                                            "Citrobacter_koseri_MINF_9D" = 1,
                                            "Enterobacter_kobei_MSB1_1B" = 2,
                                            "Haemophilus_M1C132_1" = 3,
                                            "Klebsiella_oxytoca_MSB1_2C" = 4,
                                            "Klebsiella_variicola_INF345" = 5))

ggplot(results, aes(x=polishing, y=total_distance, colour=polishing, shape=isolate)) +
  geom_point(size=2.5, stroke=2.5) +
  polisher_colours + set_shapes + guides(colour = "none") +
  theme_bw() + theme(plot.background = element_blank()) +
  scale_x_discrete(labels = display_names) +
  scale_y_continuous(trans=scales::pseudo_log_trans(),
                     breaks = c(0, 10, 100, 1000, 10000, 100000, 1000000), minor_breaks = NULL,
                     labels = c("0", "10", "100", "1000", "10000", "100000", "1000000")) +
  coord_cartesian(ylim = c(0, 1000000)) +
  labs(title = "Single-tool short-read polishing", x = NULL, y = "Sum of pairwise distances")
```

```{r}
sum(filter(results, polishing == "Trycycler+Medaka-long")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+HyPo-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+HyPo-short+HyPo-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+HyPo-short+HyPo-short+HyPo-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+NextPolish-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+NextPolish-short+NextPolish-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+NextPolish-short+NextPolish-short+NextPolish-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+ntEdit-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+ntEdit-short+ntEdit-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+ntEdit-short+ntEdit-short+ntEdit-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+Pilon-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+Pilon-short+Pilon-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+Pilon-short+Pilon-short+Pilon-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+POLCA-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+POLCA-short+POLCA-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+POLCA-short+POLCA-short+POLCA-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+Polypolish-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+Polypolish-short+Polypolish-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+Polypolish-short+Polypolish-short+Polypolish-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+Racon-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+Racon-short+Racon-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+Racon-short+Racon-short+Racon-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+wtpoa-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+wtpoa-short+wtpoa-short")$total_distance)
sum(filter(results, polishing == "Trycycler+Medaka-long+wtpoa-short+wtpoa-short+wtpoa-short")$total_distance)
```



## Greedy combination

## Round one

Already done - Polypolish was the winner.


## Round two

```{bash eval=FALSE}
__conda_setup="$('/home/ubuntu/miniconda3/bin/conda' 'shell.bash' 'hook' 2> /dev/null)"
if [ $? -eq 0 ]; then
    eval "$__conda_setup"
else
    if [ -f "/home/ubuntu/miniconda3/etc/profile.d/conda.sh" ]; then
        . "/home/ubuntu/miniconda3/etc/profile.d/conda.sh"
    else
        export PATH="/home/ubuntu/miniconda3/bin:$PATH"
    fi
fi
unset __conda_setup
conda activate hypo
for i in Acinetobacter_baumannii_J9/a Acinetobacter_baumannii_J9/b Acinetobacter_baumannii_J9/c Acinetobacter_baumannii_J9/d Citrobacter_koseri_MINF_9D/a Citrobacter_koseri_MINF_9D/b Citrobacter_koseri_MINF_9D/c Citrobacter_koseri_MINF_9D/d Enterobacter_kobei_MSB1_1B/a Enterobacter_kobei_MSB1_1B/b Enterobacter_kobei_MSB1_1B/c Enterobacter_kobei_MSB1_1B/d Haemophilus_M1C132_1/a Haemophilus_M1C132_1/b Haemophilus_M1C132_1/c Haemophilus_M1C132_1/d Klebsiella_oxytoca_MSB1_2C/a Klebsiella_oxytoca_MSB1_2C/c Klebsiella_oxytoca_MSB1_2C/d Klebsiella_variicola_INF345/a Klebsiella_variicola_INF345/b Klebsiella_variicola_INF345/c Klebsiella_variicola_INF345/d; do
    cd "$base_dir"/"$i"
    r1=reads/illumina_1.fastq.gz
    r2=reads/illumina_2.fastq.gz
    "$wrapper_dir"/hypo-short.sh trycycler__medaka-long__polypolish-short.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short__hypo-short
done
conda deactivate; conda deactivate

for i in Acinetobacter_baumannii_J9/a Acinetobacter_baumannii_J9/b Acinetobacter_baumannii_J9/c Acinetobacter_baumannii_J9/d Citrobacter_koseri_MINF_9D/a Citrobacter_koseri_MINF_9D/b Citrobacter_koseri_MINF_9D/c Citrobacter_koseri_MINF_9D/d Enterobacter_kobei_MSB1_1B/a Enterobacter_kobei_MSB1_1B/b Enterobacter_kobei_MSB1_1B/c Enterobacter_kobei_MSB1_1B/d Haemophilus_M1C132_1/a Haemophilus_M1C132_1/b Haemophilus_M1C132_1/c Haemophilus_M1C132_1/d Klebsiella_oxytoca_MSB1_2C/a Klebsiella_oxytoca_MSB1_2C/c Klebsiella_oxytoca_MSB1_2C/d Klebsiella_variicola_INF345/a Klebsiella_variicola_INF345/b Klebsiella_variicola_INF345/c Klebsiella_variicola_INF345/d; do
    cd "$base_dir"/"$i"
    r1=reads/illumina_1.fastq.gz
    r2=reads/illumina_2.fastq.gz
    "$wrapper_dir"/nextpolish-short.sh trycycler__medaka-long__polypolish-short.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short__nextpolish-short
    "$wrapper_dir"/ntedit-short.sh trycycler__medaka-long__polypolish-short.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short__ntedit-short
    "$wrapper_dir"/pilon-short.sh trycycler__medaka-long__polypolish-short.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short__pilon-short
    "$wrapper_dir"/polca-short.sh trycycler__medaka-long__polypolish-short.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short__polca-short
    # "$wrapper_dir"/polypolish-short.sh trycycler__medaka-long__polypolish-short.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short__polypolish-short
    "$wrapper_dir"/racon-short.sh trycycler__medaka-long__polypolish-short.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short__racon-short
done

for p in trycycler__medaka-long__polypolish-short__hypo-short trycycler__medaka-long__polypolish-short__nextpolish-short trycycler__medaka-long__polypolish-short__ntedit-short trycycler__medaka-long__polypolish-short__pilon-short trycycler__medaka-long__polypolish-short__polca-short trycycler__medaka-long__polypolish-short__polypolish-short trycycler__medaka-long__polypolish-short__racon-short; do
    for i in Acinetobacter_baumannii_J9 Citrobacter_koseri_MINF_9D Enterobacter_kobei_MSB1_1B Haemophilus_M1C132_1 Klebsiella_oxytoca_MSB1_2C Klebsiella_variicola_INF345; do
        cd "$base_dir"/"$i"
        printf $i"\t"$p"\t"
        "$script_dir"/pairwise_distances.py a/"$p".fasta b/"$p".fasta c/"$p".fasta d/"$p".fasta > "$p".phylip
    done
done
```

POLCA is the winner.


## Round three

```{bash eval=FALSE}
__conda_setup="$('/home/ubuntu/miniconda3/bin/conda' 'shell.bash' 'hook' 2> /dev/null)"
if [ $? -eq 0 ]; then
    eval "$__conda_setup"
else
    if [ -f "/home/ubuntu/miniconda3/etc/profile.d/conda.sh" ]; then
        . "/home/ubuntu/miniconda3/etc/profile.d/conda.sh"
    else
        export PATH="/home/ubuntu/miniconda3/bin:$PATH"
    fi
fi
unset __conda_setup
conda activate hypo
for i in Acinetobacter_baumannii_J9/a Acinetobacter_baumannii_J9/b Acinetobacter_baumannii_J9/c Acinetobacter_baumannii_J9/d Citrobacter_koseri_MINF_9D/a Citrobacter_koseri_MINF_9D/b Citrobacter_koseri_MINF_9D/c Citrobacter_koseri_MINF_9D/d Enterobacter_kobei_MSB1_1B/a Enterobacter_kobei_MSB1_1B/b Enterobacter_kobei_MSB1_1B/c Enterobacter_kobei_MSB1_1B/d Haemophilus_M1C132_1/a Haemophilus_M1C132_1/b Haemophilus_M1C132_1/c Haemophilus_M1C132_1/d Klebsiella_oxytoca_MSB1_2C/a Klebsiella_oxytoca_MSB1_2C/c Klebsiella_oxytoca_MSB1_2C/d Klebsiella_variicola_INF345/a Klebsiella_variicola_INF345/b Klebsiella_variicola_INF345/c Klebsiella_variicola_INF345/d; do
    cd "$base_dir"/"$i"
    r1=reads/illumina_1.fastq.gz
    r2=reads/illumina_2.fastq.gz
    "$wrapper_dir"/hypo-short.sh trycycler__medaka-long__polypolish-short__polca-short.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short__polca-short__hypo-short
done
conda deactivate; conda deactivate

for i in Acinetobacter_baumannii_J9/a Acinetobacter_baumannii_J9/b Acinetobacter_baumannii_J9/c Acinetobacter_baumannii_J9/d Citrobacter_koseri_MINF_9D/a Citrobacter_koseri_MINF_9D/b Citrobacter_koseri_MINF_9D/c Citrobacter_koseri_MINF_9D/d Enterobacter_kobei_MSB1_1B/a Enterobacter_kobei_MSB1_1B/b Enterobacter_kobei_MSB1_1B/c Enterobacter_kobei_MSB1_1B/d Haemophilus_M1C132_1/a Haemophilus_M1C132_1/b Haemophilus_M1C132_1/c Haemophilus_M1C132_1/d Klebsiella_oxytoca_MSB1_2C/a Klebsiella_oxytoca_MSB1_2C/c Klebsiella_oxytoca_MSB1_2C/d Klebsiella_variicola_INF345/a Klebsiella_variicola_INF345/b Klebsiella_variicola_INF345/c Klebsiella_variicola_INF345/d; do
    cd "$base_dir"/"$i"
    r1=reads/illumina_1.fastq.gz
    r2=reads/illumina_2.fastq.gz
    "$wrapper_dir"/nextpolish-short.sh trycycler__medaka-long__polypolish-short__polca-short.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short__polca-short__nextpolish-short
    "$wrapper_dir"/ntedit-short.sh trycycler__medaka-long__polypolish-short__polca-short.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short__polca-short__ntedit-short
    "$wrapper_dir"/pilon-short.sh trycycler__medaka-long__polypolish-short__polca-short.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short__polca-short__pilon-short
    "$wrapper_dir"/polca-short.sh trycycler__medaka-long__polypolish-short__polca-short.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short__polca-short__polca-short
    "$wrapper_dir"/polypolish-short.sh trycycler__medaka-long__polypolish-short__polca-short.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short__polca-short__polypolish-short
    "$wrapper_dir"/racon-short.sh trycycler__medaka-long__polypolish-short__polca-short.fasta "$r1" "$r2" trycycler__medaka-long__polypolish-short__polca-short__racon-short
done

for p in trycycler__medaka-long__polypolish-short__polca-short__hypo-short trycycler__medaka-long__polypolish-short__polca-short__nextpolish-short trycycler__medaka-long__polypolish-short__polca-short__ntedit-short trycycler__medaka-long__polypolish-short__polca-short__pilon-short trycycler__medaka-long__polypolish-short__polca-short__polca-short trycycler__medaka-long__polypolish-short__polca-short__polypolish-short trycycler__medaka-long__polypolish-short__polca-short__racon-short; do
    for i in Acinetobacter_baumannii_J9 Citrobacter_koseri_MINF_9D Enterobacter_kobei_MSB1_1B Haemophilus_M1C132_1 Klebsiella_oxytoca_MSB1_2C Klebsiella_variicola_INF345; do
        cd "$base_dir"/"$i"
        printf $i"\t"$p"\t"
        "$script_dir"/pairwise_distances.py a/"$p".fasta b/"$p".fasta c/"$p".fasta d/"$p".fasta > "$p".phylip
    done
done
```

No improvement, so we're done.



## Plot results

```{r greedy, fig.width = 6, fig.height = 3, useDingbats = FALSE}
results <- read_excel("../tables/Table_S2_real_read_results.xlsx", sheet = "Distances", col_names = TRUE)

filter(results, polishing == "Trycycler+Medaka-long" |
                polishing == "Trycycler+Medaka-long+Polypolish-short" |
                polishing == "Trycycler+Medaka-long+Polypolish-short+POLCA-short") -> results
results$polishing <- factor(results$polishing,
                            levels = c("Trycycler+Medaka-long",
                                       "Trycycler+Medaka-long+Polypolish-short",
                                       "Trycycler+Medaka-long+Polypolish-short+POLCA-short"))
display_names <- c("unpolished",
                   "Polypolish",
                   "Polypolish+POLCA")
display_names <- gsub("\\+", "+\n", display_names)

set_shapes <- scale_shape_manual(values = c("Acinetobacter_baumannii_J9" = 0,
                                            "Citrobacter_koseri_MINF_9D" = 1,
                                            "Enterobacter_kobei_MSB1_1B" = 2,
                                            "Haemophilus_M1C132_1" = 3,
                                            "Klebsiella_oxytoca_MSB1_2C" = 4,
                                            "Klebsiella_variicola_INF345" = 5))

ggplot(results, aes(x=polishing, y=total_distance, colour=polishing, shape=isolate)) +
  geom_point(size=3, stroke=2.5) +
  polisher_colours + set_shapes + guides(colour = "none") +
  theme_bw() + theme(plot.background = element_blank()) +
  scale_x_discrete(labels = display_names) +
  scale_y_continuous(trans=scales::pseudo_log_trans(),
                     breaks = c(0, 10, 100, 1000, 10000, 100000, 1000000), minor_breaks = NULL,
                     labels = c("0", "10", "100", "1000", "10000", "100000", "1000000")) +
  coord_cartesian(ylim = c(0, 15000)) +
  labs(title = "Real read greedy polishing (sum of pairwise distances)", x = NULL, y = "Errors")
```




## ALE scores

```{bash eval=FALSE}
for i in Acinetobacter_baumannii_J9 Citrobacter_koseri_MINF_9D Enterobacter_kobei_MSB1_1B Haemophilus_M1C132_1 Klebsiella_oxytoca_MSB1_2C Klebsiella_variicola_INF345; do
    for s in a b c d; do
        cd "$base_dir"/"$i"/"$s"
        r1=reads/illumina_1.fastq.gz
        r2=reads/illumina_2.fastq.gz
        for a in trycycler trycycler__medaka-long trycycler__medaka-long__hypo-short trycycler__medaka-long__hypo-short__hypo-short trycycler__medaka-long__hypo-short__hypo-short__hypo-short trycycler__medaka-long__nextpolish-short trycycler__medaka-long__nextpolish-short__nextpolish-short trycycler__medaka-long__nextpolish-short__nextpolish-short__nextpolish-short trycycler__medaka-long__ntedit-short trycycler__medaka-long__ntedit-short__ntedit-short trycycler__medaka-long__ntedit-short__ntedit-short__ntedit-short trycycler__medaka-long__pilon-short trycycler__medaka-long__pilon-short__pilon-short trycycler__medaka-long__pilon-short__pilon-short__pilon-short trycycler__medaka-long__polca-short trycycler__medaka-long__polca-short__polca-short trycycler__medaka-long__polca-short__polca-short__polca-short trycycler__medaka-long__polypolish-short trycycler__medaka-long__polypolish-short__polypolish-short trycycler__medaka-long__polypolish-short__polypolish-short__polypolish-short trycycler__medaka-long__racon-short trycycler__medaka-long__racon-short__racon-short trycycler__medaka-long__racon-short__racon-short__racon-short trycycler__medaka-long__wtpoa-short trycycler__medaka-long__wtpoa-short__wtpoa-short trycycler__medaka-long__wtpoa-short__wtpoa-short__wtpoa-short trycycler__medaka-long__polypolish-short__hypo-short trycycler__medaka-long__polypolish-short__nextpolish-short trycycler__medaka-long__polypolish-short__ntedit-short trycycler__medaka-long__polypolish-short__pilon-short trycycler__medaka-long__polypolish-short__polca-short trycycler__medaka-long__polypolish-short__racon-short trycycler__medaka-long__polypolish-short__polca-short__hypo-short trycycler__medaka-long__polypolish-short__polca-short__nextpolish-short trycycler__medaka-long__polypolish-short__polca-short__ntedit-short trycycler__medaka-long__polypolish-short__polca-short__pilon-short trycycler__medaka-long__polypolish-short__polca-short__polca-short trycycler__medaka-long__polypolish-short__polca-short__polypolish-short trycycler__medaka-long__polypolish-short__polca-short__racon-short; do
            "$wrapper_dir"/ale.sh "$a".fasta "$r1" "$r2" "$a"
        done
    done
done

# Reduce the size of the ALE output files:
cd "$base_dir"
for a in */*/*.ale; do
    grep -P "^#" "$a" > temp
    mv temp "$a"
done
```




## Detailed analysis

For some results, I wanted to manually look at the differences. E.g. when Pilon made the _Klebsiella_ distance increase, where in the genome was that happening?

To assist in this, I used Trycycler to produce a MSA of the alternative assemblies:
```{bash eval=FALSE}
t=trycycler__medaka-long__pilon-short__pilon-short__pilon-short
mkdir "$t"
for x in a b c d; do cp "$x"/"$t".fasta "$t"/"$x".fasta; done
# manually combine into a 2_all_seqs.fasta file of chromosome sequences
trycycler msa --cluster_dir "$t" --threads 32
mv "$t"/3_msa.fasta "$t".msa
rm -r "$t"
```


For _K. oxytoca_ MSB1_2C read set A, I did a read alignment (both short and long) to these assemblies:
* Polypolish+POLCA
* Polypolish+POLCA+Pilon

```{bash eval=FALSE}
cd "$base_dir"/Klebsiella_oxytoca_MSB1_2C/a
r1=reads/illumina_1.fastq.gz
r2=reads/illumina_2.fastq.gz
rl=reads/nanopore.fastq.gz

p=trycycler__medaka-long__polypolish-short__polca-short
bwa index "$p".fasta
bwa mem -t 32 "$p".fasta "$r1" "$r2" | samtools sort > "$p"__illumina.bam
samtools index "$p"__illumina.bam
rm "$p".fasta.bwt "$p".fasta.pac "$p".fasta.ann "$p".fasta.amb "$p".fasta.sa
minimap2 -a -x map-ont -t 32 --secondary=no "$p".fasta "$rl" | samtools sort > "$p"__nanopore.bam
samtools index "$p"__nanopore.bam

p=trycycler__medaka-long__polypolish-short__polca-short__pilon-short
bwa index "$p".fasta
bwa mem -t 32 "$p".fasta "$r1" "$r2" | samtools sort > "$p"__illumina.bam
samtools index "$p"__illumina.bam
rm "$p".fasta.bwt "$p".fasta.pac "$p".fasta.ann "$p".fasta.amb "$p".fasta.sa
minimap2 -a -x map-ont -t 32 --secondary=no "$p".fasta "$rl" | samtools sort > "$p"__nanopore.bam
samtools index "$p"__nanopore.bam
```

